The universal property of direct integrals in W$^*$-categories

### 2018-10-22 direct_integrals.tex
Altered the comments with my own comments.

\todo[inline]{Throughout this example, would it be better to use Borel/Baire $\sigma$-algebras instead?}

@@

\todo[inline]{This does not seem to make composition measurable}
\end{ex}

@@

\todo[inline]{Can we make the comparison more precise?}

@@

\todo[inline]{Try to construct preduals for the hom-sets in terms of spaces like $L^1(X,\cat{C}(A,B)_*)$?}
\end{proof}

@@

\todo[inline]{Is the restriction to $\sigma$-finite the ``right'' definition?}

>>>>

\todo[inline]{Throughout this example, would it be better to use Borel/Baire $\sigma$-algebras instead?

Robert: Let's not get hung up. For $\H$, Borel and Baire are the same, as its a metric space, with or without separability. In the inseparable case, the kind of measurability we need to use is inexpressible by $\sigma$-algebras on the domain and codomain anyhow. }

@@

\todo[inline]{This does not seem to make composition measurable.

Robert: Composition is measurable in the separable case, and the Borel and Baire $\sigma$-algebras of the ultrastrong and ultraweak topologies coincide. I do not expect measurability in the inseparable case for the same reason that addition of measurable functions is not measurable for inseparable-Banach-space-valued random variables. It's likely that the same solution works, however.}
\end{ex}

@@

\todo[inline]{Can we make the comparison more precise? Yetter only considers the separable case, but in this case I expect they coincide.}

@@

\todo[inline]{Try to construct preduals for the hom-sets in terms of spaces like $L^1(X,\cat{C}(A,B)_*)$? Bochner or Gelfand-Pettis integral? Since we use compact measure spaces, this only amounts to the difference between integrability of $\|f(x)\|$, \emph{i.e.} absolute integrability, vs unconditional integrability.}
\end{proof}

@@

\todo[inline]{Is the restriction to $\sigma$-finite the ``right'' definition?

Robert: As we use strictly localizable spaces, every measure space is a disjoint union of $\sigma$-finite spaces, or even finite spaces. But do you mean is $\sigma$-finite vs finite right?}
